### 2014-01-15 etc/abstract.tex
update

Explain why Random

>>>>

% 1.Statetheproblem
Mutation analysis is often used to analyze the quality of test suites. However, it has exorbitant computational requirements which makes it hard to use in practice. Operator selection, especially using only statement deletion operator has been shown to provide a close approximation to the full mutation score.
%2.Saywhyit’saninterestingproblem
However, our previous research suggests that any technique that forces accounting for the effect of each line, should achieve similar results.

%3.Saywhatyoursolutionachieves
Our research compares the mutation scores achieved using the full operator set, to that produced by a a set of operators that approximates statement deletion, and also to that produced by line based random sampling sampling.
The analysis of the resulting model shows that the line based random sampling was slightly better at approximating the original mutation score. However, this difference was not statistically significant.

%4.Saywhatfollowsfromyoursolution

This result shows that operator selection based on reduced neighborhood strategy does not have an impact on the closeness of approximation.

### 2014-01-15 src/paper.Rnw
update

\section{Related Work}
Related work.
\section{Methodology}
Our methodology

@@

avg.est <- sdl_s$coefficients['mut.avg.sdl','Estimate']
rnd.est <- rnd_s$coefficients['mut.avg.rnd','Estimate']
@

@@

@@

$ \mu_{all} = 0 + \beta_0 \times \mu_{sample}  $

The interesting part is (1) the $\beta_0$ coeff which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score   is.

@@

$ \mu_{all} = 0 + \Sexpr{avg.est} \times \mu_{sdl}  $

@@

$ \mu_{all} = 0 + \Sexpr{rnd.est} \times \mu_{rnd}  $

@@

>>>>

\section{Related Work}
Mathur\cite{mathur1991performance, wong1993mutation, wong1995reducing} first mentioned the idea of constrained mutation in a one-pager. This was taken up by Offut et al.\cite{offutt1993experimental}. (Offutt states in his 1993 paper\cite{offutt1993experimental} that Mathur has in 1991\cite{mathur1991performance} suggested the constrined/selective mutation. However, that paper does not propose it at all. It says we are experimenting with an idea, and that is it. It is in 1995\cite{wong1995reducing} that the idea is actually proposed, notably after Offutt has written about its effectiveness. $\ddot\smile$ - time travel?). The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely. They propose N-selective mutation which avoids N most fertile mutagens. Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation. According to Wong, this is different from selective mutation in that only the most fecund operators are included rather than excluded. He finds that there is no evidence to suggest one over the other. Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation. He also defines the concept of {\it operator strength} for an operator, which is defined as the total number of mutants that are killed by test data that is generated to kill only the mutants generated by that operator. He further posits that the mutagens with greatest strength may be the most useful ones. %(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)

\section{Methodology}
We collected a random sample of Java programs from Github\cite{github} that utilized the Maven\cite{maven} system for building. Next, we selected those programs from this set that passed all the unit test cases within them. We ran mutation analysis on this set of projects using PIT\cite{pitest}, with the mutators selected set to {\it all}. Because of the limitations of using a bytecode mutation engine, we could not implement statement deletion directly. Instead, we made use of the following mutation operators, that closely approximated statement deletion operator -- remove void method calls, remove non void method calls, remove conditionals, remove member variable assignments, remove increments and decrements. Finally, we modified the mutation engine to only choose one random mutation per line out of the set of applicable mutants for that line. For the second phase, we looked at the ratio between the number of mutants produced by the set of operators corresponding to statement deletion, and that of the random line mutants, and used this as a probability to add the mutants for the random line set. This was done to ensure that the results from the random sampling and statement deletion could be compared.

@@

sdl.est <- sdl_s$coefficients['mut.avg.sdl','Estimate']
rnd.est <- rnd_s$coefficients['mut.avg.rnd','Estimate']

sdl.r <- sdl_s$r.squared
rnd.r <- rnd_s$r.squared

@

@@

\begin{figure*}[t]
<<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
hist(log(10,m$pit.mutation.total.sdl), breaks=50, col=rgb(0,0,1,1/4))
hist(log(10,m$pit.mutation.num.sdl), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$pit.mutation.total.rnd), breaks=50, col=rgb(0,0,1,1/4))
hist(log(10,m$pit.mutation.num.rnd), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4))
hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
@
\caption{Plots}
\label{fig:caddrm}
\end{figure*}

@@

$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $

The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score   is.

@@

$ \mu_\{M_{all} | M_{sdl}\} = 0 + \Sexpr{sdl.est} \times M_{sdl} \text{ with } R^2 = \Sexpr{sdl.r} $

@@

$ \mu_\{M_{all} | M_{rnd}\} = 0 + \Sexpr{rnd.est} \times M_{rnd}  \text{ with } R^2 = \Sexpr{rnd.r} $

\subsection{Regression Analysis}
The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling. We can perform two statistical tests to answer this question. For the first, we run a simple paired t-test.

<<>>=
s <- t.test(mut.avg.rnd, mut.avg.sdl, paired=T)
@

The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of \Sexpr{s$p.value}. That is, we do not have sufficient evidence to conclude that the two distributions are different.

The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
Our full model is

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
<<results='asis'>>=
s <- subset(m, select=c(mut.avg,mut.avg.sdl))
s$type <- 'sdl'
colnames(s) <- c('mut', 'sample', 'type')
r <- subset(m, select=c(mut.avg,mut.avg.rnd))
r$type <- 'rnd'
colnames(r) <- c('mut', 'sample', 'type')
all <- rbind(s, r)
detach(m)
fm <- with(all, lm(mut ~ sample + type + sample:type))
sm <- anova(fm)
xtable(sm)
@

We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness. Hence, the techniques random sampling and statement deletion operator do not have any difference.

@@

The total mutants for all is \Sexpr{sum(m$pit.mutation.total)}, for rnd is \Sexpr{sum(m$pit.mutation.total.rnd)} and for sdl is \Sexpr{sum(m$pit.mutation.total.sdl)}

TODO: We should check if the distribution significantly different too.
TODO: Use sampling
TODO: Check on randoop samples too
TODO: Implement bomb (athrow) and see its mutation score, and see how close it comes.
